The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-23 conclusion.tex
Edits to conclusion and related work

\chapter{Conclusion}
We have showcased a novel approach involving black-box testing to identify the presence of E-Mail Header Injection in a web application. Using this approach, we have demonstrated that our system was able to crawl \urls\ web pages finding \forms\ forms, out of which \emailforms\ forms were fuzzable. We fuzzed \fuzzed\ forms and found \recd\  forms that allowed us to send/receive e-mails. Out of these, we were able to inject malicious payloads into \malfuzzed\ forms, identifying \success\ vulnerable forms (\successDelta\ success rate). This indicates that the vulnerability is widespread, and needs attention from both web application developers and library makers.

We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the `mail' function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application, and that the RFC's are updated to be more stringent and make it less ambiguous for future implementations.

>>>>

\section{Conclusions}
We have showcased a novel approach involving black-box testing to identify the presence of \ehi in a web application. Using this approach, we have demonstrated that our system was able to crawl \urls\ web pages finding \forms\ forms, out of which \emailforms\ forms were fuzzable. We fuzzed \fuzzed\ forms and found \recd\  forms that allowed us to send/receive e-mails. Out of these, we were able to inject malicious payloads into \malfuzzed\ forms, identifying \success\ vulnerable forms (\successDelta\ success rate). This indicates that the vulnerability is widespread, and needs attention from both web application developers and library developers.

We hope that our work sheds light on the prevalence of this vulnerability and that it ensures that the implementation of the \texttt{mail} function in popular languages is fixed to differentiate between User-supplied headers, and headers that are legitimately added by the application.

### 2016-05-23 rel_work.tex
Edits to conclusion and related work

There are different approaches to finding vulnerabilities in web applications, two of them being Black-Box testing and White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and there has been plenty of research that has made use of this methodology~\cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}. There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012}, \cite{Doupe2010}.

Our work does not intend to act as a vulnerability scanner, but as a means to identify the presence of E-Mail Header Injection vulnerabilities in a given web application. In this sense, since we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting --- XSS --- \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection~\cite{sessionride}, and is very closely related to Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.

The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g., \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.

@@

As specified before, although this vulnerability has been present for over a decade, there has not been much written about it in the literature, and we only find a few articles on the Internet describing the attack.

@@

To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability across the World Wide Web. We have managed to, on a large scale, crawl and inject websites with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website. Our injected payloads do not contain any special characters other than the newline characters and thus cannot cause any unintended consequences. Also, since we are only injecting a payload with the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load. Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify it.

>>>>

% Adam: Sai, can you combine all the \cites at the same line like I did for the others? 
There are different approaches to finding vulnerabilities in web applications, and most approaches will be either Black-Box testing or White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699}, \cite{Huang}, \cite{kals2006secubat}, \cite{payet13:ears-in-the-wild}, \cite{zanero2005automatic}. There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012}, \cite{Doupe2010}.

Our work does not intend to act as a vulnerability scanner, but as a means to identify an \ehi vulnerability in a given web application. In this sense, because we are injecting payloads into the web application, our work is related to other injection based attacks, such as SQL Injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting \cite{Injection1}, \cite{KleinAmit}, HTTP Header Injection~\cite{sessionride}, and the related Simple Mail Transfer Protocol (SMTP) Injection~\cite{Terada2015}.

The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g., \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. Terada also describes proof-of-concept attacks against certain mailing libraries such as \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper makes this observation and discusses why it is different from \ehi.

@@

Although \ehi vulnerabilities have been present for over a decade, there has not been much written about it in the literature, and we find only a few articles on the Internet describing the attack.

@@

To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability across the World Wide Web. We have managed to, on a large scale, crawl and inject web applications with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website. Our injected payloads \emph{do not contain any special characters other than the newline character} and thus cannot cause any unintended consequences. Also, because we are only injecting a payload with the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load. Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify the prevalence.
